Graph Generators: State of the Art and Open Challenges

### 2019-12-18 generators.tex
Typos fixed by Sherif

\input{generators_general}

\input{generators_LinkedData}

\input{generators_GraphDatabases}

\input{generators_SocialNetworks}

>>>>

\subsection{General Graphs}
\label{sec:generators_general}

We start by focusing on approaches that have been designed for dealing with the
generation of general graph data that is not aimed at a particular application
domain. In general, such generators focus on reproducing properties observed in
real graphs regardless of their domain such as the degree distribution, the
diameter, the presence of a large connected component, a community structure or
a significantly large clustering coefficient.

%Currently, there exists a number of tools which involve a kind of
%general graph data generator, such as gtools from projects nauty and
%Traces~\cite{gtools} or the Stanford GraphBase~\cite{GraphBase}. We, however,
%focus on primarily generating/benchmarking projects targeting the Big Data
%world.

\paragraph {Preferential Attachment} Barabasi and
Albert~\cite{Barabasi99emergenceScaling} introduced a graph generation model
that relies on two main mechanisms. The first mechanism is continuously
expanding the graphs by adding new vertices. The second mechanism is to
preferentially attach the new vertices   to the nodes/regions that are already
well connected. So, in this approach, the generation of large graphs is governed
by standard, robust self-organizing mechanisms that go beyond the
characteristics of individual applications.

\paragraph {R-MAT} R-MAT (\emph{R}ecursive \emph{Mat}rix) is a procedural
synthetic graph generator which is designed to generate power-law degree
distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.  The generator is recursive
and employs a fairly small number of parameters.  In principle, the strategy of
this generator is to achieve simple means to produce graphs whose properties correspond to
properties of the real-world graphs. In particular, the design goal of R-MAT is to
produce graphs which mimics the degree distributions, imitate a community
structure and have a small diameter. R-MAT can generate weighted, directed and
bipartite graphs.

\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph
Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} consists of a
weighted, directed graph that has a power-law distribution and four related
analysis techniques (namely graph construction, graph extraction with BFS,
                     classification of large vertex sets, and graph analysis
                     with betweenness centrality). The generator has the
following parameters: the number of nodes, the number of edges, and maximum weight of
an edge. It outputs a list of tuples containing identifiers of vertices of an
edge (with the direction from the first one to the second one) and weights
(positive integers  with a uniform random distribution) assigned to the edges of
the multigraph.  The algorithm of the generator is based on R-MAT.
%To reduce the data
%locality, the vertex ids are randomly permuted and the output
%tuples are shuffled. A related project from the same authors
%developed for the 9th DIMACS Shortest Paths Challenge is GTgraph~\cite{GTgraph}.
%t involves three types of graphs: (1) Erd\"{o}s-R\'{e}nyi random graphs, (2)
%different graphs from the DARPA HPCS SSCA\#2 graph theory benchmark
%(version 1.0), and (3) small-world graphs generated using the R-MAT graph
%generator.

\paragraph{GraphGen} For the purpose of testing the scalability of an indexing
technique called FG-index~\cite{Cheng:2007:FTV:1247480.1247574} on the size of the
database of graphs, their average size and average density, the authors have
also implemented a synthetic generator called
GraphGen\footnote{https://www.cse.ust.hk/graphgen/}. It relies on data generation code for associations and sequential
patterns provided by IBM\footnote{From 1996, no longer available at
\url{http://www.almaden.ibm.com/cs/projects/iis/hdb/Projects/data
mining/mining.shtml}}. GraphGen yields a collection of undirected, labeled and
connected graphs. It addresses the performance evaluation of frequent subgraph mining
algorithms and graph query processing algorithms. The result is represented as a
list of graphs, each consisting of a list of nodes along with a list of edges.

%\paragraph{Graph 500 Benchmark} The Graph 500 Benchmark~\cite{Graph500} includes
%a scalable data generator which produces weighted, undirected graph as a list of
%edge tuples containing the label of start vertex and end vertex together with a
%weight that represents data assigned to the edge. The space of vertex  labels is
%the set of integers beginning with 0. The input values required to describe the
%graph are (1) scale, i.e., the logarithm base two of the number of vertices, and
%(2) edge factor, i.e., the ratio of the graph's edge count to its vertex count
%(i.e., half the average degree of a vertex in the graph). The graph generator is
%a Kronecker generator similar to R-MAT. The data must not exhibit any locality,
%so in the final step the vertex labels and order of edges are randomly shuffled.
%The covered operations currently involve BFS; however, the authors intend to
%involve also two more types -- optimization (single source shortest path) and
%edge-oriented (maximal independent set) -- and five graph-related business areas:
%cybersecurity, medical informatics, data enrichment, social networks, and
%symbolic networks.

\paragraph{BTER} BTER (Block Two-Level
Erd\"{o}s-R\'{e}ny)~\cite{kolda2014scalable} is a graph generator based on the
creation of multiple Erd\"{o}s-R\'{e}ny graphs with different connection
probabilities  of which they are connected randomly between them. As the main feature, BTER is able
to reproduce input degree distributions and average clustering
coefficient per degree values. The generator starts by grouping the vertices
by degree $d$, and forming groups of size $d+1$ of nodes with degree $d$. Then, these
groups are assigned an internal edge probability in order to match the observed
average clustering coefficient of the nodes of such degree. Based on this
probability, for each node, the excess degree (i.e, the degree that in
expectation will not be realized internally in the group) is computed and used to connect
nodes from different groups at random. The authors describe a highly scalable
MapReduce-based implementation that is able to generate large graphs (consisting of
billions of nodes) in a reasonable amounts of time.

\paragraph{Darwini} Darwini~\cite{edunov2016darwini} is an extension of BTER
designed to run on Vertex Centric computing frameworks like
Pregel~\cite{malewicz2010pregel} or Apache Giraph~\cite{ching2015one}, with the
additional feature that it is more accurate when reproducing the clustering
coefficient of the input graph. Instead of just focusing on the average
clustering coefficient for each degree, Darwini is able to model the clustering
coefficient distribution per degree. It achieves this by gathering the nodes
of the graph into buckets based on the expected number of closed triangles that they need
to close in order to attain the expected clustering coefficient. The latter is
sampled from the input distributions. Then, the vertices in each bucket are
connected randomly with a probability that would produce the expected
desired number of triangles for each bucket. Then, as in BTER, the excess degree
is used to connect the different buckets. The authors report that Darwini is
able to generate graphs with billions and even trillions of edges.

%\paragraph{gtools} Projects nauty and Traces~\cite{gtools} are programs for
%computing automorphism groups of graphs and digraphs~\cite{McKay201494}; they
%can also produce a canonical label. In the respective package there is also
%suite of programs called gtools which involve generators for non-isomorphic
%graphs, bipartite graphs, digraphs, and multigraphs.

\paragraph{RTG} \emph{The Random Typing Generator} (RTG)~\cite{DBLP:journals/datamine/AkogluF09} aims at generating realistic graphs. In particular, it outputs (un)weighted, (un)directed, as well as uni/bipartite graphs, whereas the realism of the output is ensured by 11 laws (e.g., densification power law, weight power law, small and shrinking diameter, community structure, etc.) known to be typically exhibited by real-world graphs. On input it requires 4 parameters ($k$, $q$, $W$, and $\beta$) that correspond to the core Miller's observation~\cite{miller1957} that a random process (namely, having a keyboard with $k$ characters and a space, the process of random typing of $W$ words, where the probability of hitting a space is $q$ and the probability of hitting any other characters is $(1-q)/k$) leads to Zipf-like power laws (of the resulting words) plus in addition (using imbalance factor $\beta$) ensure homophily and community structure. RTG is based on the idea creating an edge between pairs of consecutive words.

Paper~\cite{DBLP:conf/wbdb/AmmarO13} further extends this idea mainly in the direction of simplification of specifying of the parameters. Instead of Miller's parameters that are not much associated with graphs, the authors prove and exploit their relationship with size and density of the target graph.

\paragraph{Strengths and Weaknesses of General Graph Generators}
In general, existing general graph generators produce graphs with the following
properties: skewed degree distribution (e.g., powerlay), small diameter, a large largest connected component, large
clustering coefficient, and some degree of
community structure. Degree distribution can be typically configured while other
properties are just a result of the generation process and cannot be controlled
by any means.

This is not the case of BTER and Darwini, which besides the degree distribution,
they also allow tuning of the clustering coefficient. However, some use cases
demand for more control on the characteristics of the generated graphs.
This is the case, for example, of benchmarking, where the underlying graph
structure has direct implications to the performance of the graph algorithms
to run. For this reason, the design of graph generators with the capability of fine
tuning the characteristics of the generated graphs still remains as an open
challenge. The questions that remain are what characteristics to tune
and which are the algorithms that depend on such characteristics.

\subsection{Semantic Web}
\label{sec:generators_LinkedData}
With the dawn of the concept of Linked Data it is a natural development that there would emerge respective
benchmarks involving both synthetic data and  data sets   with real-world characteristics.
The used data sets correspond to RDF representation of relational-like data~\cite{Guo2005158,Bizer09theberlin}, social network-like data~\cite{Schmidt2010}, or specific and significantly more complex data structures such as biological data~\cite{Wu2014}. In this section, we provide an overview of benchmarking systems involving a kind of graph-based RDF data generator or data modifier. %Other types of systems or particular results can be found, e.g., at~\cite{RdfStoreBenchmarking}.

\iffalse
Considering the Big Data world, the Linked Data in general definitely belong to this group since we assume that the Linked (Open) Data Sets form a common Linked Open Data cloud\footnote{\url{http://lod-cloud.net/}}. On the other hand, the particular data sets can be relatively small.
\fi

\paragraph{LUBM} The use-case driven Lehigh University Benchmark (LUBM)\footnote{\url{http://swat.cse.lehigh.edu/projects/lubm/}} considers the university domain. The ontology defines 43 classes and 32 properties~\cite{Guo2005158}. In addition, 14 test queries are provided in the LUBM benchmark. In particular, the benchmark focuses on \emph{extensional} queries, i.e., queries which target the particular data instances of the ontology, as an opposite to \emph{intentional} queries, i.e., queries which target properties and classes of the ontology. The Univ-Bench Artificial  (UBA) data generator features repeatable and random  data generation (exploiting classical linear congruential generator, LCG, of numbers). In particular, the data which is produced by the generator are assigned zero-based indexes (i.e., \emph{University0}, \emph{University1} etc.), thus they are reproducible at any time with the same indexes.  The generator naturally allows to specify a seed for random number generation, along with the starting index and the desired number of universities.

An extension of LUBM, the Lehigh BibTeX Benchmark (LBBM)~\cite{Wang2005}, enables generating synthetic data for different ontologies. The data generation process is managed through two main phases: (1) the property-discovery phase, and (2) the data generation phase. LBBM provides a probabilistic model that can emulate the discovered properties of the data of a particular domain and generate synthetic data exhibiting similar properties. Synthetic data are generated using a Monte Carlo algorithm. The approach is demonstrated on the Lehigh University BibTeX ontology which consists of 28 classes along with 80 properties. The LUBM benchmark includes 12 test queries that were designed for the benchmark data. Another extension of LUBM, the University Ontology Benchmark (UOBM)\footnote{\url{https://www.cs.ox.ac.uk/isg/tools/UOBMGenerator/}}, focuses on two aspects: (1) usage of all constructs of OWL Lite and OWL DL~\cite{owl} and (2) lack of necessary links between the generated data which thus form isolated graphs~\cite{Ma:2006:TCO:2094613.2094629}. In the former case the original ontology is replaced by the two types of extended versions from which the user can choose. In the latter case cross-university and cross-department links are added to create a more complex graph.

\paragraph{IIMB} Ferrara et al.~\cite{Ferrara08OM} proposed the ISLab Instance Matching Benchmark (IIMB)\footnote{\url{http://www.ics.forth.gr/isl/BenchmarksTutorial/}} for the problem of instance matching. For any two objects $o_1$ and $o_2$ adhering to different ontologies or to the same ontology, instance matching is specified in the form of a function $Om(o_1, o_2) \rightarrow \{0, 1\}$,  where $o_1$ and $o_2$ are linked to the same real-world object (in which case the function maps to $1$) or $o_1$ and $o_2$ are representing different objects (in which case the function maps to $0$). It targets the domain of movie data which contains 15 named classes, along with 5 objects and 13 datatypes. The data are extracted from IMDb\footnote{\url{http://www.imdb.com/}}. The data generator corresponds to a data modifier which simulates differences between the data. In particular it involves data value differences (such as typographical errors or usage of different standard formats, e.g., for names), structural heterogeneity (represented by different levels of depth for properties, diverse aggregation criteria for properties, or missing values specification) and logical heterogeneity (such as, e.g., instantiation on disjoint classes or various subclasses of the same superclass).

\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, is centered around an e-commerce application domain with object types such as \emph{Customer}, \emph{Vendor}, \emph{Product} and \emph{Offer} in addition to the relationship among them~\cite{Bizer09theberlin}.
The benchmark provides a workload that has 12 queries with 2 types of query workloads (i.e., 2 sequences of the 12 queries) emulating the navigation pattern and search of a consumer seeking a product. The data generator is capable of producing arbitrarily scalable datasets by controlling the number of products ($n$) as a scale factor.  The scale factor also impacts other data characteristics, such as, e.g., the depth of type hierarchy of products, branching factor, the number of product features,  etc. BSBM can output two representations, i.e. an RDF representation along with a relational representation. Thus, BSBM also defines an SQL~\cite{sql} representation of the queries. This allows comparison of SPARQL~\cite{sparql} results  to be compared against the performance of traditional RDBMSs.

\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}}
is a language-specific benchmark~\cite{Schmidt2010} which is based on the DBLP dataset. %, so the types involve Person, Inproceedings, Article etc.
The generated datasets follow the key characteristics of the original DBLP dataset. In particular, the data mimics the correlations between entities. All random functions of the generator use a fixed seed that ensures that the data generation process is deterministic. SP$^2$Bench is accompanied by 12 queries covering the various types of operators such as RDF access paths in addition to typical RDF constructs.

%\paragraph{JustBench} ~\cite{Bail:2010:JFO:1940281.1940285} ...

\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig has been designed using workloads that have been generated by applications and humans~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}. In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational-like data which is structured using a small amount of homogeneous classes, whereas, in reality, RDF datasets are tending to be more heterogeneous. For example, DBpedia 3.6 consists of 289,016 classes, whereas 275 of them are defined based on the DBpedia ontology. In addition, in property values different data types as well as references to objects of the various types are
used. Hence, they presented a universal SPARQL benchmark generation approach which uses a flexible data production mechanism that mimics the input data source. This dataset generation process begins using an input dataset; then multiple datasets with different sizes  are then generated by duplicating all the RDF triples with changing their namespaces.  For generating smaller datasets, an adequate selection of all triples is selected randomly or using a sampling mechanism over the various classes in the dataset. \iffalse The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.\fi The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 templates of SPARQL queries is derived to cover frequent SPARQL features.

\paragraph{LODIB} The Linked Open Data Integration Benchmark (LODIB)\footnote{\url{http://lodib.wbsg.de/}} has been designed with the aim of reflecting the real-world heterogeneities that exist on the Web of Data in order to enable testing of Linked Data translation systems~\cite{DBLP:conf/www/RiveroSBR12}. It provides a catalogue of 15 data translation patterns (e.g., rename class, remove language tag etc.), each of which is a common data translation problem in the context of Linked Data. The benchmark provides a data generator that produces three different synthetic data sets that need to be translated
by the system under test into a single target vocabulary. They  reflect the pattern distribution in analyzed 84 data translation examples from the LOD Cloud. The data sets reflect the same e-commerce scenario used for BSBM.

\paragraph{Geographica} The Geographica benchmark\footnote{\url{http://geographica.di.uoa.gr/}} has been designed to target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}. The benchmark involves a real-world workload that uses openly available datasets that cover various geometry elements (such as, e.g., lines, points, polygons, etc.) and  a synthetic workload. In the former case there is a (1) a micro benchmark that evaluates primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF engines in various application scenarios such as  map exploring and search (consisting of 11 queries). In the latter case of a synthetic workload the generator produces synthetic datasets of different sizes that corresponds to an ontology based on OpenStreetMap  and instantiates query templates. \iffalse The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$.\fi The generated SPARQL query workload is corresponding to spatial joins and selection using 2 query templates.

\paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)\footnote{\url{http://dsg.uwaterloo.ca/watdiv/}} has
been designed at the University of Waterloo. It implements stress testing tools that focus on addressing the observation
that the state-of-the-art SPARQL benchmarks do not fully cover the variety of queries and
workloads~\cite{Aluc:2014:DST:2717213.2717229}. The benchmark focuses on two types of query aspects --
structural and data-driven -- and performs a detailed analysis on existing SPARQL benchmarks
(LUBM, BSBM, DBPSB, and SP$^2$Bench) using these two properties of queries. The structural features involve triple
pattern count, join vertex count, join vertex degree, and join vertex count. The data-driven features involve
result cardinality and several types of selectivity. The analysis of the four benchmarks reveals that their diversity is
insufficient for evaluation of the weaknesses/strengths of the distinct design alternatives implemented by the different
RDF systems.

In particular, WatDiv, provides (1) a data generator which generates scalable datasets according to the WatDiv
schema, (2) a query template generator which produces a  set of query templates according to the WatDiv schema, and
(3) a query generator that uses the generated templates and instantiates them  with real RDF values from the dataset, and (4) a feature extractor which extracts the structural features of the generated data and workload. %For the study in the paper the authors generated 12,500 test queries from 125 query templates.

\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which receives any RDF dataset as an input and produces a set of datasets, that have similar characteristics of the input dataset, using size scaling factor $s$ and (node) degree scaling factor $d$. These factors ensure that the original RDF graph $G$ and the synthetic graph $G'$ are similar and the average node degree and the number of edges of $G'$ are changed by $s$ and $d$ respectively. \iffalse A generated benchmark dataset is considered similar to the given dataset if their values for the dataset evaluation metrics and query evaluation times for different techniques are similar. Three evaluation metrics are utilized for this purpose: dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity.\fi A query generation process has been implemented to produce 5 different types of queries (edge-based queries, node-based queries, path queries, star queries, subgraph queries) for any generated data. The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is designed to produce benchmarks from the set of sample input queries of a user-defined
size.

In practice, one way for handling big RDF graphs is to process them using the
\emph{streaming} mode where the data stream could consist of the edges of the
graph. In this mode, the RDF processing algorithms can process the input
stream in the order it arrives while using only a limited amount of
memory~\cite{mcgregor2014graph}. The streaming mode has mainly  attracted the attention of the
RDF and Semantic Web community.

\paragraph{S2Gen}   Phuoc et al.~\cite{le2012linked} presented
an evaluation framework for linked stream data processing engines. The framework
uses a datasets generated with the Stream Social network data Generator
(S2Gen), which
simulates streams of user interactions (or events) in social networks
(e.g., posts) in addition to the  user metadata such as users' profile
information, social network relationships, posts, photos and GPS information.
The data generator of this framework provides the users the flexibility to
control the characteristics of the generated stream by tanning a range of
parameters, which includes the frequency at which interactions are generated,
limits such as the maximum number of messages per user
and week, and the correlation probabilities between the different objects (e.g.,
users) in the social network.

\paragraph{RSPLab} Tommasini et al.~\cite{tommasini2017rsplab} introduced
another framework for benchmarking RDF Stream Processing systems, RSPLab. The
Streamer component of this framework is designed to publish RDF streams from the
various existing RDF benchmarks (e.g., BSBM, LUBM).
In particular, the Streamer  component uses TripleWave\footnote{\url{http://streamreasoning.github.io/TripleWave/}}, an
open-source framework which enables to share RDF streams on the
Web~\cite{mauri2016triplewave}.   TripleWave acts as a means for plugging-in
and combining streams from multiple Web data sources using either pull or push mode.

\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} %is a result of a (closed) EU project that brought together a community of academic researchers and industry that
had the goal of developing an open source, yet industrial grade benchmarks for RDF and graph databases.
\iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web
domain, it released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the
Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}). The application scenario
of this benchmark simulates a media or a publishing organization that handles large amount
of streaming content (e.g., news, articles). \iffalse This content is enriched with metadata that describes
it and links it to reference knowledge -- taxonomies and databases that include relevant concepts,
entities and factual information. The SPB data generator produces scalable in size synthetic large data.
Synthetic data consists of a large number of annotations of media assets that refer entities found in
reference datasets.\fi The data generator mimics three types of relations in the generated synthetic data:
correlations of entities, data clustering, and random tagging of entities. Two workloads are provided: (1) basic, involving an interactive query-mix querying the relations between entities in reference data, and (2) advanced,  focusing on interactive and analytical query-mixes. The LDBC has designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain.% (see Section~\ref{sec:generators_analytics}).

\paragraph{LinkGen} LinkGen is a synthetic linked data generator that has been designed to generate RDF datasets for a given vocabulary~\cite{10.1007/978-3-319-46547-0_12}. The generator is designed to receive a vocabulary as an input  and supports two statistical distributions for generating entities:  Zipf's power-law distribution and Gaussian distribution. LinkGen can augment the generated data with inconsistent and noisy  data such as updating a given datatype property with two conflicting values or  adding triples with syntactic errors. \iffalse, adding wrong statements by assigning them with invalid domain and creating instances with no type information.\fi The generator also provides a feature to inter-link the generated objects with real-world ones from user-provided real-world datasets. The datasets can be generated in any of of two modes: on-disk and streaming.

\paragraph{Strengths and Weaknesses of Semantic Web Graph Generators}  Graphs are intuitive and standard representation for the RDF model that form the basis for the Semantic Web community which has been very active on building several benchmarks, associated with graph generators that had various design principles.

A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia, the Barton Libraries Dataset~\cite{barton-benchmark} or
WordNet~\cite{Miller:1995:WLD:219717.219748}) has been reported by~\cite{Duan:2011:AOC:1989323.1989340}. The authors focus mainly on the  \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some target characteristics of each dataset. With respect to a type $T$ the degree of structuredness of a dataset $D$  is based on  the regularity of instance data in $D$ in conforming to type $T$. The type system is extracted from the data set by finding the RDF triples that have property  \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extract type $T$ from their object. Properties of $T$ are determined as the union of all properties of type $T$. The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances. The authors show that the structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets are belonging to the non-tested area of the spectrum. As a consequence, they introduce a new benchmark that receives as input any dataset associated with a required level of structuredness and size (smaller than the size of the original data), and exploits the input documents as a seed to produce a subset of the original data with the target structuredness and size. In addition, they show that structuredness and size mutually influence each other.

With the recent increasing momentum of streaming data, the Semantic Web community started to consider the issues and challenges of RDF streaming data. However, there is still a lot of open challenges that needs to tackled in this direction such as covering different real-world application scenarios.

\subsection{Graph Databases}
\label{sec:generators_GraphDatabases}

Currently there exists a number of papers which compare the efficiency of graph databases with regards to distinct use cases, such as  the community detection problem~\cite{Beis2015}, social tagging systems~\cite{Giatsoglou2011}, graph traversal~\cite{Ciglan:2012:BTO:2374486.2375242}, graph pattern matching~\cite{Pobiedina2014}, data provenance~\cite{Vicknair:2010:CGD:1900008.1900067}, or even several distinct use cases~\cite{Grossniklaus2013Towar-24253}. However, the number of graph data generators and benchmarks that have been designed specifically for graph data management systems (Graph DBMS)  is relatively small. Either a general graph generator is used for benchmarking graph databases, such as, e.g., the HPC Scalable Graph Analysis Benchmark~\cite{Dominguez-Sal:2010:SGD:1927585.1927590} or the graph DBMS benchmarking tools are designed while having in mind a more general scope. Hence it is questionable whether a benchmark  that is targeted specifically for graph databases is necessary. \cite{Dominguez-Sal:2010:DDG:1946050.1946053} discussed this question and related topics. On the basis of a review of applications of graph databases (namely, social network analysis,  genetic interactions and recommendation systems), the authors analyzed and discussed the features of the graphs for these types of applications and how such features can affect the benchmarking process, various types of operations used in these applications and the characteristics of the evaluation setup of the benchmark. In this section, we focus on graph data generators and benchmarks that have been primarily targeting graph DBMSs.

\paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible  benchmarking platform for graph databases used in cloud-based systems. Its intent is to automate
benchmarking of graph databases in the cloud by focusing on the domain social networking services. It extends the Yahoo! Cloud Multiplicative Attribute (MAG) Graph Serving Benchmark (YCSB)~\cite{Cooper:2010:BCS:1807128.1807152} and provides a set of standard workloads representing various performance issues. In particular, the workload of XGDBench involves basic operations such as read / insert / update / delete an attribute, loading of the list of neighbours and BFS traversal. Using the generators, 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.
The data model of XGDBench is a simplified version of the Multiplicative Attribute Graph (MAG)~\cite{Kim2010} model, a synthetic graph model which models the interactions between node attributes and  graph structure.
The generated graphs are thus in MAG format, with power-law degree distribution closely simulating real-world social networks.
The simplified MAG algorithm accepts the required number of nodes and for each node the number of attributes, a threshold for random  initialization of attributes, a threshold for edge affinity which determines the existence of an edge between two nodes, and an affinity matrix. \iffalse It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties.\fi
Large graphs can be generated on multi-core systems by XGDBench multi-threaded version.

\paragraph{gMark}  gMark~\cite{gMark} is a schema-driven and domain-agnostic generator of both graph instances and graph query workloads. It can generate instances under the form of N-triples and queries in various concrete query languages, including OpenCypher\footnote{\url{https://neo4j.com/developer/cypher-query-language/}}, recursive SQL, SPARQL and LogicQL. In gMark, it is possible to specify a \emph{graph configuration} involving the admitted edge predicates and node labels occurring in the graph instance along with additional parameters such as degree distribution, occurrence constraints, etc. The \emph{Query workload configuration} describes parameters of the query workload to be generated, by including the number of queries, arity, shape and selectivity of the queries.
The problem of deciding whether there exists a graph that satisfies a defined graph specification $G$ is NP-complete. The same applies to the problem of deciding
whether there exists a query workload compliant with a given query workload configuration $Q$. In view of this, gMark adopts a best effort approach in which the
parameters specified in the configuration files are attained in a relaxed fashion in order to achieve linear running time whenever possible.

%The authors prove that deciding whether there exists a graph satisfying a given graph configuration $G$ is NP-complete. And, similarly, deciding
%whether there exists a query workload satisfying a given query workload configuration $Q$ is also NP-complete. Hence, gMark generating is based on a heuristic strategy: it tries to achieve the exact values of the given parameters, however, in order to obtain linear running time it may decide to relax some. gMark generates graphs under the form of N-triples and query workloads in four concrete syntaxes, including Cypher\footnote{\url{https://neo4j.com/developer/cypher-query-language/}}, SPARQL, SQL and LogicQL.

\paragraph{GraphGen}  GraphAware GraphGen\footnote{\url{http://graphgen.graphaware.com/}} is a graph generation engine based on Neo4j's\footnote{\url{https://neo4j.com/}} query language OpenCypher~\cite{GraphGen}.  It creates nodes and relationships based on a schema definition expressed in Cypher, and it can also generate property values on both
nodes and edges. As such, GraphGen is a precursor of property graphs generators. The resulting graph can be exported to several formats (namely GraphJson\footnote{\url{https://github.com/GraphAlchemist/GraphJSON/wiki/GraphJSON}} and CypherQueries) or loaded directly to a DBMS. However, it is very likely that it is not maintained anymore due to the lack of available recent commits.

\paragraph{Strengths and Weaknesses of Graph Database Generators}
The graph DBMS generators discussed in this section have in common the fact that they can generate semantically rich labeled graphs with properties (ranging from properties values in GraphGen to MAG structures in XGDBench). They are also capable of generating graph instances and query workloads in
concrete syntaxes (among which OpenCypher in GraphGen and gMark) and one of them (XGDBench) can also handle update operations on both graph structure and content. However, more comprehensive graph DBMS generators that also produce data manipulation operations (such as updates for graph databases) are urgently needed. Additionally, none of these generators is enabled to work on corresponding query languages for property graphs, such as the newly emerging standard GQL~\cite{gql-2018} and G-Core~\cite{AnglesABBFGLPPS18}. Hence, a full-fledged graph DBMS generator for property graphs and property graph query workloads~\cite{BFVY18} is still missing and there exists an interesting opportunity to build such a generator in the near future.

Another apparent inconvenience is represented by the fact that explicit correlations among graph elements cannot be encoded for instance in gMark or GraphGen, whereas they could be fruitful in order to reproduce the behavior of real-world graphs in which attribute values are correlated one with another. On the other hand, social network and Linked Data generators that support correlations (as highlighted in Section \ref{sec:generators_socialnetworks} and Section \ref{sec:generators_LinkedData}) typically exhibit a fixed schema and are not not necessarily multi-domain as are some of the graph DBMS generators discussed in this section (namely GraphGen and gMark).

\subsection{Social Networks}
\label{sec:generators_socialnetworks}

On-line social networks, like Facebook, Twitter, or LinkedIn, have become a
phenomenon used by billions of people every day and thus providing extremely
useful information for various domains. However, an analysis of such type of
graphs has to cope with two problems: (1) availability of the data and (2)
privacy of the data. Hence, data generators which provide realistic synthetic
social network graphs are in a great demand.

In general, any analysis of social networks identifies their various specific
features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, a social
networks graph often has a high  degree of
transitivity of the graph (so-called \emph{clustering coefficient}). Or, its diameter, i.e., the longest shortest path
amongst some fraction (e.g. 90\%) of all connected nodes, is usually low due to
weak ties joining faraway cliques.

Another key aspect of social networks is the community effect. A detailed
study of structure of communities in 70 real-world networks is provided, e.g.,
in~\cite{Leskovec:2008:SPC:1367497.1367591}.
~\cite{Prat-Perez:2014:CSS:2621934.2621942} analyzed the structure of
communities (clustering coefficient, triangle participation ratio,
diameter, bridges, conductance, and size) in both real-world graphs and outputs of
existing graph generators such as LFR~\cite{PhysRevE.78.046110} and the
LDBC SNB~\cite{Erling:2015:LSN:2723372.2742786}. They found out that discovered
communities  in different graphs have common distributions and that communities
of a single graph have different characteristics and are challenging to be represented using a single
model.

The existing social network generators try to reproduce different aspects of the
generated network. They can be categorized into statistical and agent-based.
\emph{Statistical
approaches}~\cite{PhysRevE.78.046110,Yao2011,Armstrong:2013:LDB:2463676.2465296,Pham2013,Sukthankar-SocialInfo2014,Erling:2015:LSN:2723372.2742786,Nettleton2016}
focused on reproducing aspects of the network. In \emph{agent-based
approaches}~\cite{Barrett:2009:GAL:1995456.1995598,Bernstein:2013:SAS:2499604.2499609}
the networks are constructed by directly simulating the agents' social choices.

%\paragraph{LFR} Lancichinetti, Fortnato and Radicchi (hence
%LFR)~\cite{PhysRevE.78.046110} develop a class of benchmark graphs whose nodes
%participate in internal community structures. The benchmark models directed and
%weighted real-world networks (e.g., social networks) containing overlapping
%communities of different sizes. The algorithm assumes that both the degree and
%the community size distributions are power laws. Each node shares a fraction $(1
%- \mu)$ of its links with the other nodes of its community and a fraction $\mu$
%with the other nodes of the network, where $\mu$ is called \emph{mixing
%parameter}. The sizes of the communities are taken from a power law distribution
%such that the sum of all sizes equals the number of nodes of the graph. The
%generation process starts with an empty graph and incrementally fills in the
%adjacency matrix by obeying the described constraints.

\paragraph{Realistic Social Network}
~\cite{Barrett:2009:GAL:1995456.1995598} focused on the construction of
realistic social networks. For this purpose the authors combine both
private and public data sets with large-scale agent-based techniques. The process works as
follows: In the first step it generates  synthetic data by combining public and
commercial databases. In the second step, it determines a set of activity
templates. A 24-hour activity sequence including geolocations is assigned to
each synthetic individual. To demonstrate the approach, the authors create a
synthetic US population consisting of people and households together with
respective geolocations. For this purpose the authors combine simulation and
data fusion techniques utilizing various real-world data sources such as U.S.
Census data, responses to a time-use survey or an activity survey.
%Demographic information for each person and location, a minute-by-minute
%schedule of each person's activities, and the locations where these activities
%take place is generated by a combination of simulation and data fusion
%techniques.
The result is captured by a dynamic network of social contacts. Similar methods for
agent-based strategies have been reported
in~\cite{Bernstein:2013:SAS:2499604.2499609}.
